The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-04-15 paper/iphas-dr2.tex
Messing with Table 5

@@

L. Huckvale$^{15}$,

@@

C. Knigge$^{16}$,
T. Kupfer$^{5}$, \newauthor
D. J. Lennon$^{17}$,

@@

R. A. H. Morris$^{18}$,
T. Naylor$^{19}$, \newauthor
Q. A. Parker$^{20,21,22}$, 
S. Phillipps$^{17}$, 

@@

P. Rodr\'\i guez-Gil$^{6,7}$,
L. Sabin$^{23}$, \newauthor
S. Scaringi$^{24,25}$,

@@

Y. C. Unruh$^{26}$, 
J. van Roestel$^5$,
K. Viironen$^{27}$, \newauthor
J. S. Vink$^{28}$, 

@@

$^{15}$Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of Manchester, Manchester M13 9PL, U.K.\\
%$^{16}$School of Physics \& Astronomy, University of Southampton, Southampton, SO17 1BJ, U.K.\\
%$^{17}$European Space Astronomy Centre (ESAC), Villafranca del Castillo, Villanueva de la Canada, E-28692 Madrid, Spain.\\
%$^{18}$School of Physics, Bristol University, Tyndall Avenue, Bristol, BS8 1TL, U.K.\\
%$^{19}$School of Physics, University of Exeter, Stocker Road, Exeter, EX4 4QL, U.K.\\
%$^{20}$Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia.\\
%$^{21}$Australian Astronomical Observatory, PO Box 915, North Ryde, NSW 1670, Australia.\\
%$^{22}$Research Centre for Astronomy, Astrophysics and Astrophotonics, Macquarie University, Sydney, NSW 2109 Australia.\\
%$^{23}$Instituto de Astonom\'ia y Meteorolog\'ia, Departamento de F\'isica, CUCEI, Universidad de Guadalajara, Mexico.\\
%$^{24}$Instituut voor Sterrenkunde, K.U. Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium.\\
%$^{25}$Max-Planck-Institut f\"ur extraterrestrische Physik (MPE), Giessenbachstrasse 1, D-85748, Garching bei M\"unchen, Germany. \\
%$^{26}$Department of Physics, Blackett Laboratory, Imperial College London, Prince Consort Road, London, SW7 2AZ, U.K.\\
%$^{27}$Centro de Estudios de F\'isica del Cosmos de Arag\'on, Plaza San Juan 1, Planta 2, Teruel, 44001, Spain. \\
%$^{28}$Armagh Observatory, College Hill, Armagh, Northern Ireland, BT61 9DG, U.K.\\
$^{16-28}$ (affiliations 16 to 28 are given in the source file)

@@

A total of 219 million primary detections satisfied
the above criteria and have been included in the catalogue.
Amongst these, 158 million objects 
are detected in all three bands (72 per cent),
30 million are detected in two bands (14 per cent),
and 31 million entries are single-band detections (14 per cent).
Half of the single-band detections were made in the $i$-band.
This is because $i$ is least
affected by interstellar extinction and can occasionally pick up
highly-reddened objects which are otherwise lost in $r$ and \ha.
Moreover, late-type stars tend to be intrinsically brighter in $i$.

\begin{table}
    \caption{Detection statistics.}
    \label{tbl:detections}
        \begin{tabular}{lrcrrr}
        \toprule
        Detection & N & \%($nObs>1$) &
        $\overline{pStar}$ & $\overline{(r-i)}$ & $\overline{(r-\ha)}$ \\
        \midrule
        $r$, $i$, \ha & 159 (73\%) & 91\% & 0.82 & 1.03 & 0.44  \\
        $r$, $i$ (not \ha) & 25 (11\%) & 77\% & 0.70 &  1.26 & - \\
        $i$, \ha\ (not $r$) & 3 (1\%) & 73\% & 0.49 &  & \\
        $r$, \ha\ (not $i$) & 2 (1\%) & 65\% & 0.53 & - & 0.58 \\
        only $i$ & 15 (7\%) & 43\% & 0.44 \\
        only $r$ & 9 (4\%) & 27\% & 0.42 \\
        only \ha & 6 (3\%) & 12\% & 0.11 \\
        \midrule
        Total & 219 & 81\% \\
        \bottomrule
        \end{tabular}
\end{table}

@@

The catalogue is made available on our website (www.iphas.org)
as a collection of binary FITS tables,
each covering a $5\degr\times5\degr$ tile
of the survey footprint.
The catalogue can be queried in two ways.
First, it is made available through the
Vizier on-line service (http://vizier.u-strasbg.fr)
where it can be queried using their web interface
or using Virtual Observatory (VO) protocols.
Second, on our website we provide a script
to ingest the binary FITS tables into a
{\sc PostgreSQL} database on a user's computer.

The website also provides access to the pipeline-processed
imaging data, which we have updated to include
a new keyword {\sc photzp},
which contains the re-calibrated zeropoint.
It can be used to convert the number counts $DN$
-- which are the pixel values -- 
into Vega-based magnitudes $m$ using:
\begin{equation}
\begin{split}
   m  = \textsc{photzp} - 2.5 \log_{10}(DN)
\label{eqn:mag}
\end{split}
\end{equation}
That is, the {\sc photzp} has been computed such that it
absorbs the required corrections for atmospheric extinction,
gain variations, exposure time, and the re-calibration shift
derived in this work.

>>>>

A. A. Henden$^{15}$,

@@

L. Huckvale$^{16}$,

@@

C. Knigge$^{17}$, \newauthor
T. Kupfer$^{5}$, 
D. J. Lennon$^{18}$,

@@

R. A. H. Morris$^{19}$, \newauthor
T. Naylor$^{20}$, 
Q. A. Parker$^{21,22,23}$,
S. Phillipps$^{19}$, 

@@

P. Rodr\'\i guez-Gil$^{6,7}$, \newauthor
L. Sabin$^{24}$, 
S. Scaringi$^{25,26}$,

@@

Y. C. Unruh$^{27}$, 
J. van Roestel$^5$, \newauthor
K. Viironen$^{28}$, 
J. S. Vink$^{29}$, 

@@

$^{15}$AAVSO, 49 Bay State Road, Cambridge, MA 02138, USA.\\
%$^{16}$Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of Manchester, Manchester M13 9PL, U.K.\\
%$^{17}$School of Physics \& Astronomy, University of Southampton, Southampton, SO17 1BJ, U.K.\\
%$^{18}$European Space Astronomy Centre (ESAC), Villafranca del Castillo, Villanueva de la Canada, E-28692 Madrid, Spain.\\
%$^{19}$School of Physics, Bristol University, Tyndall Avenue, Bristol, BS8 1TL, U.K.\\
%$^{20}$School of Physics, University of Exeter, Stocker Road, Exeter, EX4 4QL, U.K.\\
%$^{21}$Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia.\\
%$^{22}$Australian Astronomical Observatory, PO Box 915, North Ryde, NSW 1670, Australia.\\
%$^{23}$Research Centre for Astronomy, Astrophysics and Astrophotonics, Macquarie University, Sydney, NSW 2109 Australia.\\
%$^{24}$Instituto de Astonom\'ia y Meteorolog\'ia, Departamento de F\'isica, CUCEI, Universidad de Guadalajara, Mexico.\\
%$^{25}$Instituut voor Sterrenkunde, K.U. Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium.\\
%$^{26}$Max-Planck-Institut f\"ur extraterrestrische Physik (MPE), Giessenbachstrasse 1, D-85748, Garching bei M\"unchen, Germany. \\
%$^{27}$Department of Physics, Blackett Laboratory, Imperial College London, Prince Consort Road, London, SW7 2AZ, U.K.\\
%$^{28}$Centro de Estudios de F\'isica del Cosmos de Arag\'on, Plaza San Juan 1, Planta 2, Teruel, 44001, Spain. \\
%$^{29}$Armagh Observatory, College Hill, Armagh, Northern Ireland, BT61 9DG, U.K.\\
$^{16-29}$ (affiliations 16 through 29 are given in the source file)

@@

A total of 219 million primary detections satisfied
the above criteria and have been included in the catalogue.
Amongst these, 159 million are detected 
in all three bands (73 per cent),
30 million are detected in two bands (14 per cent),
and the remaining 30 million are single-band detections.
The detailed breakdown is presented in Table~\ref{tbl:detections},
along with the fraction of `confirmed' sources,
hich we define
as objects which were detected in more than
one field pointing (usually the alternative pointing of a field pair).
Sources detected in all three 
(Table~\ref{tbl:detections}).
Half of the single-band detections were made in the $i$-band.
This is most likely because $i$ is least
affected by interstellar extinction and can occasionally pick up
highly-reddened objects which are otherwise lost in $r$ and \ha.
Table~\ref{tbl:detections} also shows the fraction of the
sources that were `confirmed', w
For the class of 
in more than one field (usually the field observed at the small offset position)

\begin{table}
    \caption{Breakdown of catalogue entries as a function of the band(s) in which the source was detected. We also show the fraction of `confirmed' objects, which we define as sources which were detected in more than one field pointing (usually the field pair partner). Also included are the mean magnitudes for each class.}
    \label{tbl:detections}
        \begin{tabular}{lrcccc}
        \toprule
        Band(s) & Sources & Confirmed & $\overline{r}$ & $\overline{i}$ & $\overline{\ha}$ \\
        & [$10^6$] & [\emph{nObs}$>$1] & [mag] & [mag] & [mag] \\
        \midrule
        $r$, $i$, \ha & 159 & 91\% & 19.3 & 18.2 & 18.8  \\
        $r$, $i$ & 25 & 77\% & 21.2 & 19.9 & - \\
        $i$, \ha & 3 & 73\% & - & 19.6 & 20.2 \\
        $r$, \ha & 2 & 65\% & 20.6 & - & 20.1 \\
        $i$ & 15 & 43\% & - & 19.8 & - \\
        $r$ & 9 & 27\% & 21.1 & - & - \\
        \ha & 6 & 12\% & - & - & 19.9 \\
        \midrule
        Total  & 219 & 81\% & 19.6 & 18.6 & 18.9 \\
        \bottomrule
        \end{tabular}
\end{table}

@@

The catalogue is made available on our website (www.iphas.org)
as a collection of binary FITS tables,
each covering a $5\degr\times5\degr$ tile
of the footprint.
The catalogue can be queried in two ways.
First, will be made available through the
Vizier on-line service (http://vizier.u-strasbg.fr),
where it can be accessed using a web interface
and using Virtual Observatory (VO) protocols.
Second, on our website we provide a script
to ingest the binary FITS tables into a
{\sc PostgreSQL} database for users
who wish to mine the data locally.

The website also provides access to the pipeline-processed
imaging data, which we have updated to include
a new keyword, called {\sc photzp},
which contains the re-calibrated zeropoint.
The keyword can be used to convert the number counts $DN$,
which stored in the pixel values,
into Vega-based magnitudes $m$ using:
\begin{equation}
\begin{split}
   m  = \textsc{photzp} - 2.5 \log_{10}(DN).
\label{eqn:mag}
\end{split}
\end{equation}
That is, {\sc photzp} has been computed such that it
absorbs the required corrections for atmospheric extinction,
gain variations, exposure time, and the re-calibration.

A user will only have to apply a correction
for the flux lost outside
